Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-06 doc/main_jfm.tex
some changes (fig captions)

\begin{figure}
\begin{center}
  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  JP vesicles suspended in a shear flow. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Two JP vesicles suspended in
  an extensional flow. The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the JP vesicles. The flow rate is $\chi = 0.005$ in all cases.
  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left JP vesicle is $0.1$ units above the $x$-axis
  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
  the left JP vesicle is $0.1$ units above the $x$-axis and the right
  JP vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
  the left JP vesicle is $0.5$ units above the $x$-axis and the
  centroid of the right JP vesicle is $0.5$ units below the $x$-axis.
  Figure~\ref{figure12} presents the numerical results from the case
  (iii).}
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.9\textwidth]{ShearTraj.eps}
\end{center} 
  \caption{\label{figure9} The shape and trajectories of two
  JP vesicles suspended in a shear flow. The moving paths of the two
  centroids are plotted in blue and red. The centroids are initially
  located on the $x$-axis. For simulation time, $t = {0, 400,800,1200}$
  for (a)--(d) and $t = {1600, 2400, 3200, 4000}$ for (e)--(h).
  The fluid velocity profile is plotted in the background.
  }
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Two JP vesicles suspended in
  an extensional flow. The moving paths of the two centroids are plotted
  in blue in red. Each row corresponds to a different initial placement
  of the JP vesicles. The flow rate is $\chi = 0.005$ in all cases.
  (i) Both JP vesicle centroids are on the $x$-axis. (ii) The
  centroid of the left JP vesicle is $0.1$ units above the $x$-axis
  and the right JP vesicle is on the $x$-axis. (iii) The centroid of
  the left JP vesicle is $0.1$ units above the $x$-axis and the right
  JP vesicle is $0.1$ units below the $x$-axis. (iv) The centroid of
  the left JP vesicle is $0.5$ units above the $x$-axis and the
  centroid of the right JP vesicle is $0.5$ units below the $x$-axis.
  Figure~\ref{figure12} presents the numerical results from the case
  (iii).  The fluid velocity profile is plotted in the background.}
\end{figure}
